seqwish: inducing pangenome graphs

### 2021-12-21 manuscript/main.tex
andrea++

    \title[seqwish: inducing pangenome graphs]{seqwish: inducing pangenome graphs}
    \author[Garrison \textit{et~al}.]{
        Erik~Garrison\,$^{\text{\sfb 1}*}$
    }

    \address{
        $^{\text{\sf 1}}$University of Tennessee Health Science Center, Memphis, TN, USA
    }

>>>>

    \title[seqwish: inducing pangenome graphs]{seqwish: inducing pangenome graphs}
    \author[Garrison \textit{et~al}.]{
        Erik~Garrison\,$^{\text{\sfb 1}*}$,
        Andrea~Guarracino\,$^{\text{\sfb 2}}$
    }

    \address{
        $^{\text{\sf 1}}$University of Tennessee Health Science Center, Memphis, TN, USA \\
        $^{\text{\sf 2}}$Genomics Research Centre, Human Technopole, Milan, Italy
    }
